RJObject Paper

### 2014-06-22 Documents/Paper/ms.tex
CDF etc

\subsection{Proposals that modify objects}

>>>>

\subsection{Proposals that modify objects}
Let $F(x | \alpha)$ be the cumulative distribution corresponding to the interim
prior $p(x | \alpha)$, and $F^{-1}(x | \alpha)$ its inverse.
Then $F(x_i)$ (for all $i$) has a uniform prior between 0 and 1. A proposal
for an object involves transforming its parameters to $[0, 1]$ using $F^{-1}$,
make the proposal, and then transform back.
